---
title: "K-Prototypes: A Case Study"
author: 
output: github_document

---

$$\alpha, \beta,  \gamma, \Gamma$$

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
```

### Erik's Practical Applications of Unsupervised Learning

1.  Initial exploratory: How many groups of people, places, companies,
    things just naturally exist in this data?
2.  Feature engineering - map multiple features to a smaller, discrete
    categorical variable which can then be plugged in as a more simple
    predictive feature
3.  Target engineering - Once I have found these natural categories
    exist, can I then use them as my Y and predict future membership in
    that cluster?
<div>

</div>
## A K-Means Refresher

K-Means clustering is a classic algorithm used for clustering that attempts to find the center of $k$ specified clusters

## Why K-Prototypes?

The problem with K-Means clustering



You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
